---
title: "410 Project V2"
author: "Frank D'Ambrosio"
date: "4/28/2021"
output: html_document
---
Libraries
```{r}
library(dplyr)
library(plyr)
library(ggplot2)
library(ggpubr)
library(rms)
library(VGAM)
library(MASS)
library(gam)
library(lmtest)
library(tree)
library(randomForest)
library(rpart)
library(rpart.plot)
library(party)

```

import data set
```{r}
admission <- read.csv("Admission_Predict.csv" )
head(admission)

```

GOALS:
find significance of variables that go into the rating of university that a student applies to
  -the variables known by the student before they apply is their GRE.Score, CGPA, TOEFL.Score, and Research
  -predict university rating applied to based on these variables
      -Cumulitive Logit model for University.Rating
      
Significance of variables for Chance.of.Admit
  -create a GLM for predicting Chance.of.Admit using all significant variables and University.Rating as levels?



Let's make a model for predicting chance of admission
```{r}

#str(admission)
#get rid of serial number
ad2 <- subset(admission, select=c(Chance.of.Admit, GRE.Score, TOEFL.Score, University.Rating, SOP, LOR, CGPA, Research))
ad2$Research <- as.factor(ad2$Research)
str(ad2)
attach(ad2)
ad.frame <- data.frame(GRE.Score, TOEFL.Score, University.Rating, SOP, LOR, CGPA, Research )

#bestglm(ad.frame, IC = "BIC")

fit1 <- glm(Chance.of.Admit ~ . , data=ad2 , family = quasibinomial)
summary(fit1)
#SOP not significant

fit2 <- glm(Chance.of.Admit ~ . -SOP, data=ad2, family = quasibinomial)
summary(fit2)

fit3 <- glm(Chance.of.Admit ~ . - SOP - University.Rating, data = ad2, family = quasibinomial)
summary(fit3)


lrtest(fit3, fit2)

nested <- glm(Chance.of.Admit ~ . - SOP - University.Rating, data=ad2 , family = quasibinomial)
complex <- glm(Chance.of.Admit ~ GRE.Score + TOEFL.Score + LOR + University.Rating + Research + CGPA, data=ad2 , family = quasibinomial)
lrtest(nested, complex)

#get rid of uni rating
summary(nested)
fit.final <- nested
summary(fit.final)


plot(fit.final)
plot(ad2)

set.seed(7492)
indices <-  sample(300,100)
T1 <- ad2[indices,]
T2 <- ad2[-indices,]


fit <- glm(Chance.of.Admit ~. -University.Rating - SOP, data = T1 , family =  quasibinomial)

preds <- predict(fit, T2)

mse <- mean((preds-T2$Chance.of.Admit)^2)
#mse = .41225

exp(range(preds))/(1+ exp(range(preds)))
```

Why is University rating insignificant in this model?
```{r}
attach(ad2)




ad.ur <- ggboxplot(admission, x = "University.Rating",
          y = "Chance.of.Admit",
          bgcolor="black",
          color = "University.Rating",
          palette = c("darkgreen" , "blue", "purple", "orange", "red")
          )
ad.ur +
  bgcolor("#BFD5E3")+
  border("#BFD5E3")


cor.test(Chance.of.Admit, University.Rating)
#we can see University and Chance are strongly correlation with a pvalue 2.2e-16




#check out GPA
g.ur.GPA <- ggboxplot(admission, x = "University.Rating",
          y = "CGPA",
          bgcolor="black",
          color = "University.Rating",
          palette = c("darkgreen" , "blue", "purple", "orange", "red")
          )
g.ur.GPA +
  bgcolor("#BFD5E3")+
  border("#BFD5E3")

cor.test(CGPA, University.Rating)

#now we see CGPA and Uni rating are closely correlated with pvaly also 2.2e-16

#look at GRE Score
g.ur.GRE <- ggboxplot(admission, x = "University.Rating",
          y = "GRE.Score",
          bgcolor="black",
          color = "University.Rating",
          palette = c("darkgreen" , "blue", "purple", "orange", "red")
          )
g.ur.GRE +
  bgcolor("#BFD5E3")+
  border("#BFD5E3")

cor.test(GRE.Score, University.Rating)

#GRE Score and University rating are closely correlated too.

#now TOEFL.Score

g.ur.TOEFL <- ggboxplot(admission, x = "University.Rating",
          y = "TOEFL.Score",
          bgcolor="black",
          color = "University.Rating",
          palette = c("darkgreen" , "blue", "purple", "orange", "red")
          )
g.ur.TOEFL +
  bgcolor("#BFD5E3")+
  border("#BFD5E3")

cor.test(TOEFL.Score, University.Rating)


```

Can we predict University Rating by the above three
```{r}
attach(ad2)
ad2$University.Rating <- as.ordered(ad2$University.Rating)
set.seed(7492)
indices = sample(300,100)
T1 <- ad2[indices,]
T2 <- ad2[-indices,]
str(T1)
str(T2)

tree1 <- tree(as.ordered(University.Rating)~ CGPA + GRE.Score , data = T1,  mincut=3  )
summary(tree1)
plot(tree1)
text(tree1)

x <- ctree((as.ordered(University.Rating)~ CGPA + GRE.Score + Chance.of.Admit ))
plot(x, type = "simple")

prp1 <- rpart(as.ordered(University.Rating)~ CGPA + GRE.Score ,  data = T1,minbucket = 3 )
#text(prp1)
rpart.plot(prp1, tweak = 1.9, box.palette = list("darkgreen" , "blue", "purple", "orange", "red"))


rf1 <- randomForest(as.ordered(University.Rating)~ CGPA + GRE.Score + TOEFL.Score , data = T1, ntree=280 , mtry=2)
#plot(rf1)

summary(rf1)

preds <- predict(rf1, T2)


mse <- mean((as.numeric(preds)-as.numeric(T2$University.Rating))^2)

mse
#MSE of 0.8333 but with the levels only ranging 1-5 this might still be big



```













